Documentation FFI Sonar Simulator

### 2013-05-22 FFI-Simulator/ffi-simulator.tex
la2pdf commit - 2013:05:23	00:48:31	(Thu23.May)

As detailed below, in this revision we have decided to opt for slightly more flexibile design to better be able to handle effects such as geometric layover.
% This is to better be able to simulate geometrical sonar imaging effects such as layover. We will describe both the original suggestions and the updated design here.

@@

\subsection{Geometrical Layover}

@@

>>>>

As detailed below, in this revision we have decided to add a couple alternative designs that is more flexible and able to handle effects such as geometric layover and multipath.
% This is to better be able to simulate geometrical sonar imaging effects such as layover. We will describe both the original suggestions and the updated design here.

@@

\subsection{Layover and multipath}

When using OpenGL, there is

@@

\begin{figure}[b]
\begin{narrow}{-2.3cm}{-2.3cm}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_setup.png}
\end{narrow}
\caption{Two possible implementation strategies.}\label{implementation}
\end{figure}
